---
title: "Regression models course assignment"
author: "Siva"
date: "February 27, 2016"
output: pdf_document
---

<h1> Assignment Case Study - Regression Models Course Project - Motor Trend </h1>

<li> You work for Motor Trend, a magazine about the automobile industry.</li>
<li> Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). </li> 
<li> They are particularly interested in the following two questions: </li>

<li> 1. "Is an automatic or manual transmission better for MPG" </li>
<li> 2. "Quantify the MPG difference between automatic and manual transmissions" </li>

<h2> Case study with solution step by step : </h2>

<p> First, we load the dataset mtcars and lets preview the dataset beforehand 
using header command. </p>

```{r}
library (datasets)
data(mtcars)
head(mtcars)
```

<p> Model Vs and am columns as categorical variables </p>

```{r}
mtcars$vs <- as.factor(mtcars$vs)
mtcars$am <- as.factor(mtcars$am)
```

<li> View the summary of variable mpg </li>
```{r}
summary(mtcars$mpg)
```

<p> Draw a quick boxplot to understand the relationship between variable mpg and variable am.
The boxplot shows clear diffierence between both variables. 
In order to prove this signifcat difference we would need to perform addtional exploratory analysis.
Next steps would be understand how these variables behave as liner regression model and mulitvariate regression models </p>

```{r, echo=FALSE}
boxplot(mpg ~ am, data = mtcars, xlab = "Transmission type")
```

<h2> Simple linear regression model </h2>

<p> Try to fit using linear regression model </p>

```{r}
fit_simple <- lm(mpg ~ factor(am), data=mtcars)
summary(fit_simple)
```

<p> P Values is 0.000285 and R - square adjusted value is 33.85 % 
which leaves us with question of how the remainaing models behaves and hence not a best fit model. </p>

<h2> Multivariable Regression Model</h2>
```{r}
data(mtcars)
fit_multi <- lm(mpg ~ . ,data=mtcars)
summary(fit_multi)
```


```{r, echo=FALSE}
cor(mtcars)[1,]

fit_final <- lm(mpg ~ wt+hp+disp+cyl+am, data = mtcars);

par(mfrow = c(2, 2))
plot(fit_final)
```

<p> The adjusted R- Square value is 80.66 % which is closer to our expectation and multivariate models 
fits best for this mtcars dataset.
I have ploted residuals and check for non normality behavior.
From the first graph, we can observe that the variance is almost the same across.
we can see that the multiple R squared value is much higher at 0.85 in third graph using the final high impacting variables.</p>


<h2> Conclusion : </h2> 
<p> The 'wt' and 'cyl'are confounding variables in the relationship between 'am and 'mpg' 
and that manual transmission cars on average have 1.55 miles per gallon more than automatic cars.
1. "Is an automatic or manual transmission better for MPG" : Answer Manual transssion 
2. "Quantify the MPG difference between automatic and manual transmissions" : Manual cars have 1.55 miles per gallan mpg compared to an automatic transmission. </p>



